---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# linearregression.packages

<!-- badges: start -->
[![R-CMD-check](https://github.com/kyokaono8811/linearregression/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kyokaono8811/linearregression/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of linearregression.packages is to run a simple/multiple linear regression to understand the relationship between covariates and a response variable. 

## Installation

You can install the development version of linearregression.packages from [GitHub](https://github.com/) with: 

``` r
# install.packages("pak")
pak::pak("kyokaono8811/linearregression")
```

## Usage

This demonstrates how to use the function with a dataset (mtcars)

```{r example}
library(linearregression.packages)
```

```{r}
library(datasets)
data(mtcars)
head(mtcars)
```

```{r}
Y <- mtcars$hp
X <- cbind(mtcars$wt, mtcars$drat)
```

```{r}
linearregression(X,Y)
```


